sem

### 2022-12-07 scripts/workshop/sem.Rmd
Update sem.Rmd
shipley example

```{r}
dSep(sem)
summary(sem)
```

>>>>

```{r}
dSep(sem)
summary(sem)
```
Lefcheck example

```{r}
data(shipley)
```

```{r}
dd_lat <-  lme(DD~lat, random = ~1|site/tree, na.action = na.omit, 
    data = shipley)

date_dd <-lme(Date~DD, random = ~1|site/tree, na.action = na.omit, 
    data = shipley)

growth_date <-  lme(Growth~Date, random = ~1|site/tree, na.action = na.omit, 
    data = shipley)

live_growth <-  glmer(Live~Growth+(1|site)+(1|tree), 
    family=binomial(link = "logit"), data = shipley)
```

```{r}
shipley_sem <- psem(dd_lat, date_dd, growth_date, live_growth)
```

```{r}
summary(shipley_sem)
```
